QPLIB: A Library of Quadratic Programming Instances

### 2018-01-30 QPLIB-3.tex
extend caption of Figure 5
- Hessian is only half
- explain what red means

\begin{figure}
\centering
\includegraphics[scale=0.5]{{QPLIB_2967.jac}.png} \qquad
\includegraphics{{QPLIB_2967.hess}.png}
\caption{Example for the sparsity pattern of the Jacobian of the constraint functions (left) and
  of the Hessian of the Lagrangian function (right) for instance QPLIB\_2967.
  The gradient of the objective function is displayed as the first row
  of the Jacobian matrix.}
\label{fig:sparsitypattern}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.5]{{QPLIB_2967.jac}.png} \qquad
\includegraphics{{QPLIB_2967.hess}.png}
\caption{Example for the sparsity pattern of the Jacobian of the constraint functions (left) and
  of \textcolor{red}{the upper-right triangle of} the Hessian of the Lagrangian function (right) for instance QPLIB\_2967.
  The gradient of the objective function is displayed as the first row
  of the Jacobian matrix. \textcolor{red}{Non-constant entries are shown in red.}}
\label{fig:sparsitypattern}
\end{figure}
